Contention Management for 5G

### 2017-05-17 article/article.tex

      We assume the weight of the central arc to be $0$ since it appears in every route,
      its value does not matter when considering affectations.\\
      Collisions between messages can only appear at node $c_s$ on the way forward and at node $c_t$ on the way back.
      Thus, we only have to check if there is no collisions in a period at those two points.
      We consider two periods P at these vertices, the the {\bf forward period} at $c_s$, and the {\bf backward period} at $c_t$. A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1}) \mod P$ in the forward period, and  $c_t$ at time $m_{t_1} + t(c_t,r_{t_1})\mod P$ in the backward period.
      A $(P,\tau)$-periodic affectation consist in choosing for all $i < n$, $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$, we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$.

@@

  In this subsection, we deal with a simpler version of the problem PALL.
  We ask for a $(P,\tau)$-periodic affectation {\bf with all waiting times equal to $0$} and we call this restricted problem  
  {\bf Periodic Assignment for Zero Latency} or PAZL. 
  In that case $MT({\cal M})$ is equal to twice the delay of the longest route, thus $T_{max}$ is not relevant anymore. 
  Since $w_i=0$, choosing $m_i$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i) \mod P$.
 We assume from now on that the weight of the arcs from $s_i$ to $c_s$ are all equal to $0$, since we can change 
  all $m_i$ into $m_i - t(c_s,r_i) \mod P$ and obtain the same affectation.

@@

      \begin{proposition} When $n\tau + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0})) \leq P$, the algorithm Shortest-Longest solves PAZL.
      \end{proposition}
      \begin{proof}
       Since $m_{s_i} = i\tau$, $[t(c_s,r_{s_i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.

       We assume that $\lambda(r_{s_0}) = 0$, by removing $\lambda(r_{s_0})$ to every route, it does not change the order on the routes
       nor the result of this algorithm.
      We have  $[t(c_s,r_{t_i})] = \{2 \lambda(r_{s_i}) + i\tau, \dots,  2 \lambda(r_{s_i}) + (i+1)\tau -1\}$ since $2 \lambda(r_{s_{n-1 }}) + n\tau \leq P$.
       Since $ \lambda(r_{s_i}) \leq  \lambda(r_{s_{i+1}})$ by construction, we have  $2 \lambda(r_{s_i}) + (i+1)\tau -1 < 2 \lambda(r_{s_{i+1}}) + (i+1)\tau$
       which proves that there are no collision on the backward period. 
      \end{proof}

      If the period is slightly smaller that the bound, a collision will occur on the route in the backward period, making 
      this policy not useful even as a heuristic for longer routes.

%       
% The message using the shortest route is sent before the others, therefore on the backward period it cannot conflict 
% 
% comes back to the central node before the following ones.
% Then, the second message is sent before the others, and also will be back before the third etc... 
% Because the message $i$ is sent $\tau$ slots after the message $i-1$ ($m_{s_i} = m_{s_{i-1}} + \tau$), it comes back after the end of the message $i-1$: $m_{s_{i-1}}+ \tau + 2.\lambda(r_{s_{i-1}}) \le m_{s_i} + 2.\lambda(r_{s_i})$ because of $\lambda(r_{s_i}) \ge \lambda(r_{s_{i-1}})$.
% 
%       Because of $m_{s_i} = \tau.i$ in the forward period, there is no collisions.
%       To ensure that there is no collisions in the backward period, we must ensure that the last message ends before the end of the period P. We have to find the minimum period P such that the last message have totally came back before P slots after the first message.
%       
%       The this policy ensure us a period of $$P = \tau * n + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0}))$$ if routes $\{r_0,...,r_{s_{n-1}}\}$ are ordered
% from the shortest to the longest. 
% 
% We have to calculate the time taken by the last message to reach $c_t$. $2.\lambda(r_{s_0})$ is the first slot in which the first message is coming back in the backward period,
% and 2$\lambda(r_{s_{n-1}}) + n . \tau $ is the time at which the last message has totally passed the switch.
% Therefore, the period only depends of the difference between the longest and the shortest route: the larger this value is, the larger
% the period is.
%

@@

    \begin{proposition}
    Let  $n$ be the number of routes and let $ 3n\tau \leq P$, then there is an algorithm which finds a $(P,\tau)$-periodic affectation in time $O(n^2)$.
    \end{proposition}
    \begin{proof}
     We consider the forward period and cut it into consecutive macro slots of $\tau$ time slots. The algorithm works by choosing an offset for each route in the following way: try all offests which put the message in a yet not used macro slot in the forward
     period. The choice of an offset also fixes the position of the message in the backward period, chose the first one which does not create a collision. We now prove that this algorithm always find an offset for all routes when $P \geq 3n\tau$.

     Assume we are choosing the offset of the route $r_{k+1}$, we have  at least $P - k \geq 3n - k$ free macro-slots, since $P \geq 3n\tau$. Each of these $3n - k$ possible offset values translates into $3n - k$ positions of messages in the backward period. All these positions are separated by at least $\tau$ slots. There are already $k$ messages of size $\tau$ in the backward period. One such message can intersect at most $2$ potential positions since they are disjoint intervals. Therefore  amongst the possible $3n - k$ positions, there are  $3n - k -2k$ which are without collision. Since $k < n$, one of the choice is without collision, which proves that the algorithm terminates and find a  $(P,\tau)$-periodic affectation.

@@

      \begin{center}
      \includegraphics[scale=0.3]{ex3nt.png}
      \end{center}
% 	\begin{algorithm}[H]
% 	\caption{Greedy affectation}
% 	\begin{algorithmic}
% 	\REQUIRE ${\cal R}_{\cal C}$, period $P$
% 	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
% 	\STATE $T$ a table of the macro slots of size $\tau$ in the forward period.
% 	\STATE $L$ a list of free intervals in the backward period%$P2[P]$ slots backward period.
% 	\FORALL{source $s$ in S}
% 
% 	\FORALL{free intervals $[a,b]$ in $L$}
% 	\FORALL{ $a/\tau - \lambda(s) <j< b/\tau - \lambda(s)$ }
% 	\IF{ $T[j] == FREE$}
% 	\STATE $m_{s} \leftarrow j.\tau$
% 	\STATE $T[j] = USED$
% 	\STATE update $[a,b]$ in $L$
% 	\STATE BREAK
% 	\ENDIF
% 	\ENDFOR
% 	\ENDFOR
% % 	
% % 	\IF{No intervals are found for $s_i$}
% % 	\STATE return FAILURE
% % 	\ENDIF
% % 	\ENDFOR
% 
% 	\ENDFOR
% 
% 	\end{algorithmic}
% 	\end{algorithm}
\todo{J'ai commencé à modifier l'algo pour qu'il colle, mais ça n'est pas encore ça. 
pas sur que ça vaille la peine de le mettre, je le commente pour l'instant.}

This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
In fact, experimental data in Subsection~\ref{sec:experimental_results} suggest that the algorithm works well as soon as $P \geq 1.5 \tau$ for small routes.

\todo{vérifier cette affirmation en faisant une expérience et une régression linéaire}

@@

% 	    
      We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found
      a $(P,\tau)$-periodic affectation. We have $n$ routes denoted by $\{0,\dots,n-1\}$. A partial solution $S$ is 
      a partial function from $[n]$ to $\{0,1,\dots,P-\tau -1\}$ which sets a starting time for a subset of the routes $R(S) \subseteq [n]$,
      such that there are no collisions for these routes.  A partial solution $S'$ extends $S$, if it sets one more routes than $S$ to a larger starting time than all routes in $S$, that is $R(S') = R(S) \cup \{r'\}$ and for all  $r \in R(S)$, $S(r) + \tau \leq S'{r'}$. We define a tree whose nodes are partial solutions and such that the root is the empty partial solution and 
      the children of a partial solution are the partial solutions which extend it. All solutions to our problem will be 
      leaves in this tree, therefore our algorithm is simply a depth-first search of the tree.

      Remark that a node $S$ with $|R(S)| = k$ can have as many as $(n-k)P$ children. Since the tree is of depth $n$, the tree may have as many as $n!P^n$ elements and while $n$ is often small, $P$ may be large which makes its traversal intractable.  Therefore we have to find cuts in the tree to avoid to explore it entirely and henceforth make the algorithm practical. Cuts correspond to the detection of subtrees which contain no solutions and can thus be skipped.   
      We now propose three cuts, the first two being particularly useful when the network is loaded ($n\tau$ is not much smaller than $P$).

@@

       \item 
       For the next two cuts, we need to define the notion of the useful slots of a partial solution $S$ in the \emph{backward period}: a slot is said to be useful, if it is not used by a message set by $S$ in the backward period and it belongs to an interval of at least $\tau$ such slots. Useful slots are positions which can be used when extending $S$. We will denote by $([a_i,b_i[)_{i\leq l}$ the ordered sequence of intervals of useful slots of $S$. Without loss of generality we can assume that all $a_i, b_i \leq l$. The number of message of size $\tau$ which can be set in the useful slots of $S$ is thus  $\displaystyle{ \sum_{i=0}^{l} (b_{i} -a_i)/\tau } $. If that value is less than the number of routes which are not in $R(S)$, it is a failure and the algorithm backtracks. Notice that the list of intervals of useful slots and the value $\displaystyle{ \sum_{i=0}^{l} (b_{i} -a_i)/\tau } $ can be maintained in constant time, since each time a route is added, we only need to split an interval of useful slots into at most two such intervals.

       \item 
       Let $S_1$ and $S_2$ be two partial solutions with $R(S_1) = R(S_2)$. Let $US_1$ (respectively $US_2$) be the set of useful slots of $S_1$ (resp. $S_2$). We say that $S_1$ dominates $S_2$ if the largest offset fixed in $S_1$ is smaller than the one in $S_2$ and $US_2 \subseteq US_1$. Remark that any valid sequence of extension of $S_2$ (fixing offsets of routes in the complementary of 
       $R(S_2)$) is also a valid sequence of extensions of $S_1$. Therefore if the tree rooted at $S_2$ contain a solution, then $S_1$ contains one too. Hence, in our exhaustive search of the tree of partial solutions, we can skip the tree rooted at $S_2$.

       We now explain how we can detect some partial solutions which are dominated so that we do not explore their subtrees.
       Consider a partial solution $S$ which we extend into $S'$ by setting the offset of the route $r$ to be the smallest possible. The offset of $r$ in the backward period is $S'(R)+ \lambda$ and we denote the end of the message before before by $a$. Then all extensions of $S$ into $S''$ with $S'(r)  < S''(r) < a + \tau - \lambda$ are dominated by $S'$. Therefore when computing the extension of $S$, we first build $S'$ and then $S''$ with $S''(r) =  a + \tau - \lambda$ , skipping all values in between.

@@

      The third cut works well in conjunction with the first one since it makes the offsets grow quickly and 
      which makes the first cut more likely to apply. A last cut could be implemented, by computing whether for every 
      route not in $R(S)$ the set of possible positions in the backward period and checking whether one s contained in the useful slots of $S$.

@@

      The following performance evaluation results compares the three presented algorithms.
      Notice that both Greedy algorithm and the Shortest-Longest are polynomial time algorithm but are not always able to
      find optimal solutions. On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time.
      We will compare the performance of the algorithms in two different regimes: the routes are either short or arbitrary long.
%             
%             The graphs 
%       To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU. The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route. The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.

      \todo{Mettre les données concrètes plus proprement et éventuellement ne pas les mettre si on envoie pas à un truc de télécom}

@@

      Firstly, we made some performance evaluation on graphs in which the values $\lambda(c_t,r_{t_i})$ are drawn uniformly between $0$ and $700$ slots. This parameter is coming from our C-RAN context, in which the physical links are short enough. In C-RAN context, the size of a message is of $2500$ slots.\\

      For a given instance, we try to determine the minimum period $P$ for which the graph has a $(P,\tau)$ periodic affectation; to that end,  we need to do a linear search on the value $P$, a dichotomy would not work because of Lemma~\ref{lemma:monotonic}.
      We generated $1000$ random instances of PAZL, and we applied the linear search with each of the three algorithm. Then we measure the average minimal period, for each algorithm. We applied this test increasing the number of routes, until it was too long for the exhaustive search to find a solution quickly.

%our network has a throughput of 10Gbps throughput and 
%       
%       
%       The messages size $\tau$ is of 2500 slots, that is, approximately 1.228 Gbps of data for each route. The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.

      Since the exhaustive search is optimal, the average periods founds by this algorithm is the lower lower bounds for the other algorithms.
      As an information, we draw the $f(n) = n\tau$, which is an absolute lower bound on the period and $g(n) = 3n\tau$ lines which is the theoretical upper bound of the greedy algorithm.

@@

% 	  We now consider waiting times. The weights on links from sources to $c_s$ are now relevant because the goal is to minimize $MT({\cal M})$, with ${\cal M}$ the $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$.
% 	  To build such a $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, we must choose the offsets $m_{s_i}$ and $m_{t_i}$, such that there is no $PT(s)$ greater than a given $T_{max}$.
% 	  As a reminder, $ PT(s)=\lambda(r_s)+ w_s+\lambda(r_{t_i})$.

>>>>

      We assume the weight of the central arc to be $0$ since it appears in every route,
      its value does not matter when considering affectations.\\
      Collisions between messages can only appear at node $c_s$ on the way forward and at node $c_t$ on the way back.
      Thus, we only have to check if there is no collisions in a period at those two points.
      We consider two periods P at these vertices, the the {\bf forward period} at $c_s$, and the {\bf backward period} at $c_t$. A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1}) \mod P$ in the forward period, and  $c_t$ at time $m_{t_1} + t(c_t,r_{t_1})\mod P$ in the backward period.

      A $(P,\tau)$-periodic affectation is the choice for all $i < n$, of $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$, we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$.

@@

  In this subsection, we deal with a simpler version of the problem PALL.
  We ask for a $(P,\tau)$-periodic affectation {\bf with all waiting times equal to $0$} and we call this restricted problem {\bf Periodic Assignment for Zero Latency} or PAZL. 
  In that case $MT({\cal M})$ is equal to twice the delay of the longest route, thus $T_{max}$ is not relevant anymore. 
  Since $w_i=0$, choosing $m_i$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i) \mod P$.
  Remark that there is a bijection between the affectation of a star topology and the 
  the affectation of the same star topology where all arcs from $s_i$ to $c_s$ have weight equal to $0$
  by changing $m_i$ into $m_i - t(c_s,r_i) \mod P$. Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.

  \todo{Dire qu'on donne deux algos qui trouvent toujours une solution quand certains condtions sont remplies
  et un dernier qui sait décider si il y a une solution oui ou non mais qui est exponentiel avec des optimisations pour le rendre pratique}

@@

      \begin{proposition} When $n\tau + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0})) \leq P$,
      the algorithm Shortest-Longest solves positively PAZL in time $O(n\log(n))$.\label{prop:SL}
      \end{proposition}
      \begin{proof}
       Since $m_{s_i} = i\tau$, $[t(c_s,r_{s_i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.

       We assume may that $\lambda(r_{s_0}) = 0$, since removing $\lambda(r_{s_0})$ to every route does not change the order on the length of the routes and thus the result of this algorithm.
      We have  $[t(c_s,r_{t_i})] = \{2 \lambda(r_{s_i}) + i\tau, \dots,  2 \lambda(r_{s_i}) + (i+1)\tau -1\}$ since $2 \lambda(r_{s_{n-1 }}) + n\tau \leq P$.
       Since $ \lambda(r_{s_i}) \leq  \lambda(r_{s_{i+1}})$ by construction, we have  $2 \lambda(r_{s_i}) + (i+1)\tau -1 < 2 \lambda(r_{s_{i+1}}) + (i+1)\tau$ which proves that there are no collision on the backward period.

       The complexity of the algorithm is dominated by the sorting of the routes. 
      \end{proof}

      If the period is slightly smaller that the bound of Proposition~\ref{prop:SL}, a collision will occur on the route in the backward period, making 
      this policy not useful even as a heuristic for longer routes.

@@

    \begin{proposition}
    Let  $n$ be the number of routes and let $ 3n\tau \leq P$, then there is an algorithm which positively solves PAZL in time $O(n^2)$.
    \end{proposition}
    \begin{proof}
     We consider the forward period and cut it into consecutive interval of size $\tau$ that we call macro-slots. The algorithm works by choosing an offset for each route in the following way: try all offsets which put the message in a yet not used macro-slot in the forward
     period. The choice of an offset also fixes the position of the message in the backward period, chose the first one which does not create a collision. We now prove that this algorithm always finds a $(P,\tau)$-periodic affectation without waiting time when $P \geq 3n\tau$.

     Assume we are choosing the offset of the route $r_{k+1}$, we have at least $P - k \geq 3n - k$ free macro-slots in the forward period, since $P \geq 3n\tau$. Each of these $3n - k$ possible offset values translates into $3n - k$ positions of messages in the backward period. All these positions are separated by at least $\tau$ slots. There are already $k$ messages of size $\tau$ in the backward period. One such message can intersect at most $2$ potential positions since they are disjoint intervals. Therefore  amongst the possible $3n - k$ positions, there are  at least $3n - k -2k$ which are without collision. Since $k < n$, $3n - k -2k \geq 1$, which proves that the algorithm terminates and find a  $(P,\tau)$-periodic affectation.

@@

      \begin{center}
      \includegraphics[scale=0.3]{ex3nt.png}
      \end{center}
% 	\begin{algorithm}[H]
% 	\caption{Greedy affectation}
% 	\begin{algorithmic}
% 	\REQUIRE ${\cal R}_{\cal C}$, period $P$
% 	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
% 	\STATE $T$ a table of the macro slots of size $\tau$ in the forward period.
% 	\STATE $L$ a list of free intervals in the backward period%$P2[P]$ slots backward period.
% 	\FORALL{source $s$ in S}
% 
% 	\FORALL{free intervals $[a,b]$ in $L$}
% 	\FORALL{ $a/\tau - \lambda(s) <j< b/\tau - \lambda(s)$ }
% 	\IF{ $T[j] == FREE$}
% 	\STATE $m_{s} \leftarrow j.\tau$
% 	\STATE $T[j] = USED$
% 	\STATE update $[a,b]$ in $L$
% 	\STATE BREAK
% 	\ENDIF
% 	\ENDFOR
% 	\ENDFOR
% % 	
% % 	\IF{No intervals are found for $s_i$}
% % 	\STATE return FAILURE
% % 	\ENDIF
% % 	\ENDFOR
% 
% 	\ENDFOR
% 
% 	\end{algorithmic}
% 	\end{algorithm}

This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
In fact, experimental data in Subsection~\ref{sec:experimental_results} suggests that the algorithm works well as soon as $P \geq 1.5 \tau$.

@@

% 	    
      We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found a $(P,\tau)$-periodic affectation. Contrarily to the two previous algorithms, when it fails to find a solution, then it certifies there are no solution to PAZL.

      We have $n$ routes denoted by $\{0,\dots,n-1\}$. A partial solution $S$ is 
      a partial function from $[n]$ to $\{0,1,\dots,P-\tau -1\}$ which sets a starting time for a subset of the routes $R(S) \subseteq [n]$, such that there are no collisions for these routes.  A partial solution $S'$ extends $S$, if $S'$ is defined over one more route than $S$ and this route has a larger starting offset than all routes of $S$: $R(S') = R(S) \cup \{r'\}$ and for all  $r \in R(S)$, $S(r) + \tau \leq S'{r'}$. We define a tree whose nodes are partial solutions and such that the root is the empty partial solution and 
      the children of a partial solution are the partial solutions which extend it. The solutions to our problem will be the leaves of depth $n$ in the tree, therefore our algorithm is a depth-first search of the tree.

      Remark that a node $S$ with $|R(S)| = k$ can have as many as $(n-k)P$ children. Since the tree is of depth $n$, the tree may have as many as $n!P^n$ elements and while $n$ is small, $P$ may be large which makes its traversal intractable.  Therefore we have to find cuts in the tree to avoid to explore it entirely and henceforth make the algorithm practical. Cuts correspond to the detection of subtrees which contain no solutions and can thus be skipped.   
      We now propose three cuts, the first two being particularly useful when the network is loaded ($n\tau$ is not far from $P$).

@@

       \item 
       For the next two cuts, we need to define the notion of the useful slots of a partial solution $S$ in the \emph{backward period}: a slot is said to be useful, if it is not used by a message set by $S$ in the backward period and it belongs to an interval of at least $\tau$ such slots. Useful slots are positions which can be used when extending $S$. We will denote by $([a_i,b_i[)_{i\leq l}$ the ordered sequence of intervals of useful slots of $S$. Without loss of generality we can assume that all $a_i, b_i \leq l$. The number of messages of size $\tau$ which can be placed in the useful slots of $S$ is thus  $\displaystyle{ \sum_{i=0}^{l} (b_{i} -a_i)/\tau } $. If that value is less than the number of routes which are not in $R(S)$, it is a failure and the algorithm backtracks. Notice that the list of intervals of useful slots and the value $\displaystyle{ \sum_{i=0}^{l} (b_{i} -a_i)/\tau } $ can be maintained in constant time, since each time a route is added, we only need to split an interval of useful slots into at most two such intervals.

       \item 
       Let $S_1$ and $S_2$ be two partial solutions with $R(S_1) = R(S_2)$. Let $US_1$ (respectively $US_2$) be the set of useful slots of $S_1$ (resp. $S_2$). We say that \emph{$S_1$ dominates $S_2$} if there are more useful slots both in the forward and backward periods for $S_1$ than for $S_2$. Formally, the largest offset fixed in $S_1$ is smaller than the one in $S_2$ and $US_2 \subseteq US_1$. Remark that any valid sequence of extensions of $S_2$ (choosing offsets of routes in the complementary of $R(S_2)$) is also a valid sequence of extensions of $S_1$. Therefore if the tree rooted at $S_2$ contain a solution, then $S_1$ contains one too. Hence, in our exhaustive search of the tree of partial solutions, we can skip the tree rooted at $S_2$.

       We now explain how we can detect some partial solutions which are dominated so that we do not explore their subtrees.
       Consider a partial solution $S$ which we extend into $S'$ by setting the offset of the route $r$ to be the smallest possible. The offset of $r$ in the backward period is $S'(r)+ \lambda$ and we denote the end of the message before before by $a$. Hence all extensions of $S$ into $S''$ such that $S'(r)  < S''(r) < a + \tau - \lambda$ are dominated by $S'$. Therefore when computing the extension of $S$, we first build $S'$ and then $S''$ with $S''(r) =  a + \tau - \lambda$ , skipping all values in between.

@@

      The third cut works well in conjunction with the first one since it makes the offsets grow quickly and 
      which makes the first cut more likely to apply. A last cut could be implemented: compute for every route not in $R(S)$ the set of possible positions in the backward period and verify whether at least one is contained in the useful slots of $S$.

@@

      The following experimental results help compare the three presented algorithms.
      Notice that both Greedy algorithm and the Shortest-Longest are polynomial time algorithm but are not always able to find a solution. On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time. We will compare the performance of the algorithms in two different regimes: the routes are either short with regards to $\tau$ and $P$ or unrestricted.
      We choose the parameter realistic with regard to our C-RAN context. The number of routes 
      is at most $n = 20$, $\tau$ is equal to $2500$ and the period is at most $3n\tau$ (otherwise the greedy algorithm always returns a solution).

      \todo{Dire où on peut trouver le code (pas la peine de donner des infos sur la machine/compilateur car one ne fait pas d'étude de performances.}
%             
%             The graphs 
%       To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU. The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route. The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.
% 
%       \todo{Mettre les données concrètes plus proprement et éventuellement ne pas les mettre si on envoie pas à un truc de télécom}

@@

      First we consider routes which are shorter than $\tau$, that is a message cannot be contained 
      completely in a single edge. This is typical in our context and we will consider graphs in which the values $\lambda(c_t,r_{t_i})$ are drawn uniformly between $0$ and $700$ slots. It corresponds to messages of size blah and links of bandwidth 10Gbps and length less than blah.

      \todo{à compléter}

      Our aim is to understand how well the algorithms are working when the network has a high load (when 
      the load is low, the greedy algorithm always returns a solution). To do that we try to evaluate the 
      minimal period for which a $(P,\tau)$ periodic affectation can be found by each algorithm. 
      To that end we do a linear search on $P$, since a dichotomy would not work because of Lemma~\ref{lemma:monotonic}.

      In our experiment, we generated $1000$ random instances of PAZL for $1$ to $12$ routes. 
      We measured the average minimal period, for each algorithm. We needed to stop our experiments at $12$ routes since the exhaustive search was taking more than a second to finish on many instances.
      Note that the exhaustive search is optimal, that is it finds the best possible period for a given instance. 
      We also drew the function $f(n) = n\tau$, which is an absolute lower bound on the period and $g(n) = 3n\tau$ which is the theoretical upper bound of the greedy algorithm.

@@

% 
%
